---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h1 {
  color: #be6000;
  font-family: Helvetica;
  font-size: 45px;
}
h2 {
  color: #006000;
  font-family: Helvetica;
  font-size: 35px
}

p {
  color: #6a6e4d;
  font-size: 20px;
  line-height: 1.5;
  font-family: Helvetica;
}

body {
  background-color: #EEEEEE;
  padding: 30px 0;
}

hr {
  border: none;
  border-top: .7px solid #6a6e4d; /* Line color and thickness */
  margin: 20px 0;
}

```

# Overview
## Instagram Reels Analysis and Viewer Behavior Trends

---

This report explores data collected on Instagram reels, analyzing factors such as reel count, genres, time of day, and reasons for engagement. By examining these aspects, it provides insights into user behavior and preferences.

All data in this report was gathered via Google Forms through observational logging.

```{r}
# Load necessary libraries
library(tidyverse)

# Load the CSV data into a data frame
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTvz1IslYYgWxg1L7GxmT0zM-PWKdosPGqrrou2ok9s0zvuNKxvEv7e-px9Os0KO7gvfPU-39niKz80/pub?output=csv"
logged_data <- read_csv(csv_file)
#logged_data

# Renaming variables for clarity through creating a new data frame called latest_data
latest_data <- logged_data %>%
  rename(
    Reel_Count = `How many Instagram reels did you watch during this session?`, 
    Genre = `What genre best describes the reel/s you observed?`,
    Time_of_Day = `What time of the day did you observe the reel/s?`,
    Reasons = `What made the reel/s stand out to you?`,
  )

# Calculate summary values which is the mean of of Reel_Count
mean_reel_counts_value <- mean(latest_data$Reel_Count, na.rm = TRUE)
rounded_mean <- round(mean_reel_counts_value, 2) # Round mean to 2 decimal places

genre_counts <- latest_data %>%
  count(Genre) %>% # Count the occurrences of each genre
  arrange(desc(n)) # Arrange in descending order of frequency

# View the genre with the highest count
most_popular_genre <- genre_counts %>%
  slice(1)

# Extracting genre name and count from the most_popular_genre data frame
genre_name <- most_popular_genre$Genre
genre_count <- most_popular_genre$n

# Find the Time_of_Day with the highest total_count
most_active_time <- latest_data %>%
  group_by(Time_of_Day) %>%
  summarise(total_count = sum(Reel_Count, na.rm = TRUE)) %>%
  arrange(desc(total_count)) %>%
  slice(1)

# Extract the Time_of_Day and its count
most_active_time_of_day <- most_active_time$Time_of_Day
most_active_time_reel_count <- most_active_time$total_count
```

---

# Summary Insights

---

## Average Number of Reels Watched Per Session

The average number of reels watched per session is **`r rounded_mean`**, indicating how many reels users engage with during typical sessions.

## Most Popular Genre

The most frequently observed genre is **`r genre_name`**, appearing **`r genre_count`** times in the dataset. This highlights user preferences for this genre.

## Most Common Time for Reel Watching

The time of day with the highest reel engagement is **`r most_active_time_of_day`** with a total of **`r most_active_time_reel_count`**, indicating which time of day I scroll through my Instagram account the most.

# Bar Charts

---

## Total Instagram Reel Engagement by Time of Day

---

```{r}
# Create a bar chart to visualize a categorical variable which is time_frame
reel_count_bar_chart <- latest_data %>%
  group_by(Time_of_Day) %>%
  summarise(total_count = sum(Reel_Count, na.rm = TRUE)) %>%
  ggplot(aes(x = Time_of_Day, y = total_count, fill = Time_of_Day)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Total Instagram Reel Engagement by Time of Day",
    x = "Time of Day",
    y = "Total Reel Count",
    fill = "Time of Day"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(reel_count_bar_chart)

```

This bar chart depicts the correlation between the time of day when reels were viewed (x-axis) and the overall count of reels (y-axis). Each bar indicates the total number of reels viewed during a designated time frame, with distinct colors used to differentiate these periods for better understanding. The visualization highlights peak engagement times, revealing when users are most active with Instagram reels, which provides essential insights for determining the best times to post in order to enhance audience reach and interaction. The design is clean and minimalistic, promoting ease of reading and effective analysis.

## Distribution of Instagram Reel Genres Across Time Periods

---

```{r}
# Create a stacked bar chart with Time_of_Day and Genre
stacked_bar_chart <- latest_data %>%
  count(Time_of_Day, Genre) %>% # Summarize counts
  ggplot(aes(x = Time_of_Day, y = n, fill = Genre)) + 
  geom_bar(stat = "identity") + # Create stacked bars
  labs(
    title = "Distribution of Instagram Reel Genres Across Time Periods",
    subtitle = "Analysing the amount of reels observed with different genres at a given time",
    x = "Time of Day",
    y = "Reel Count",
    fill = "Genre",
    caption = "Source: Google Forms",
  ) +
  theme_minimal() + # Clean theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels

# Print the stacked bar chart
print(stacked_bar_chart)

```

This stacked bar chart illustrates the distribution of Instagram reel genres at various times throughout the day. The x-axis indicates distinct time intervals (such as morning, afternoon, and evening), while the y-axis shows the number of reels recorded for each genre. Each bar is divided by genre, offering a detailed overview of genre preferences during these times. This visualization enables us to discern which genres capture user interest during peak viewing hours and emphasizes the variety of content engagement across different periods. Such insights could prove beneficial for customizing content strategies to align with specific audience preferences.
